
```{r setup, warning=FALSE, include=FALSE, echo=FALSE, message=FALSE, output=FALSE}
library(knitr)
library(kableExtra)
library(formattable)

source('_code/wrc-api.R')
source('_code/wrc-wrangling.R')
source('_code/wrc-charts.R')
source('timing_sketches.R')
```

```{r setup_logger, echo=FALSE}
logFile = file("build.log", 'w') 
cat("Starting build", file=logFile, sep='\n')
```

```{r init_vars, warning=FALSE, include=FALSE, echo=FALSE, message=FALSE, output=FALSE}
# Load in event data (moved to index.Rmd)
#s = get_active_season()
#eventId = get_eventId_from_name(s, 'italia')
#rally_name = paste0(s[s$id==eventId,'name'], ", 2021")

itinerary = get_itinerary(eventId)
sections = get_sections(itinerary)
controls = get_controls(sections)

stages = get_stages(sections) #status and code are useful...

stages$cum_dist = cumsum(stages$distance)
stages$start_dist = c(0, stages$cum_dist[-length(stages$cum_dist)])


stages_lookup = get_stages_lookup(stages)

stage_cols = c('stageId', 'number', 'name', 'distance', 'code')
stage_info = stages %>%
                select(all_of(stage_cols)) %>%
                # Tidy up the stage name
                mutate(name = str_replace(name, ' \\(Live TV\\)', ''))
  
# For driver details
entries = get_rally_entries(eventId)
cars = get_car_data(entries)

# We can have customer entries which mess things up...
# TO DO - need to look this up properly

class_WRC_exclusions = c("C. FERAUD", "L. BERTELLI",
                         "J. SERDERIDIS")
class_WRC = cars %>% filter(groupname=='Rally1')  %>% 
                filter(!(drivername %in% class_WRC_exclusions)) %>% 
                select(entryId) 


class_WRC2 = cars %>% 
                  filter(startsWith(eligibility, 'WRC2')) %>%
                  select(entryId)

class_JWRC = cars %>% filter(eligibility=='JWRC') %>% select(entryId)

class_WRC3 = cars %>% filter(eligibility=='WRC3') %>% select(entryId)

#wrc = cars %>% filter(entryId<=22519)

result_group = 'WRC'

if (result_group == 'WRC') {
  target_class = class_WRC
} else if (result_group == 'WRC2') {
  target_class = class_WRC2
} else if (result_group == 'WRC3') {
  target_class = class_WRC3  
} else if (result_group == 'JWRC') {
  target_class = class_JWRC
} else target_class = class_WRC

use_group_rank = TRUE

wrc = cars %>% filter(entryId %in% target_class$entryId)
wrc_entries = wrc$entryId
```

```{r save_metadata, echo=FALSE}
save_data = function(df, fn, dirpath = "results_data/") {
  if (!dir.exists(dirpath))
      dir.create(dirpath, recursive=TRUE)

  write.csv(df, file.path(dirpath, fn), row.names = FALSE)
}

#save_data(cars, "cars.csv")
#save_data(controls, "controls.csv")
#save_data(entries %>% select(-eventClasses, -tags), "entries.csv")
#save_data(stage_info, "stage_info.csv")
#save_data(stages, "stages.csv")
#save_data(wrc, "wrc.csv")
```

```{r done_setup, echo=FALSE}
cat("Done setup", file=logFile, sep='\n')
```

# Overall Standings {-}

*Summary reports of overall standings and stage results.*

```{r main_overall_report, message=FALSE, echo=FALSE, error=FALSE, warning=FALSE, results='asis'}
#stage_list=list("SS1", "SS2", "SS3", "SS4", "SS5", "SS6", "SS7", "SS8", "SS9", "SS10", "SS11", "SS12", "SS13", "SS14", "SS15", "SS16", "SS17", "SS18", "SS19", "SS20")
#stage_list=list("SS1", "SS2", "SS3", "SS4", "SS5", "SS6", "SS7", "SS8", "SS9","SS10", "SS11", "SS12", "SS13", "SS14", "SS15", "SS16", "SS17", "SS18", "SS19")
stage_list=list("SS1", "SS2", "SS3", "SS4", "SS5", "SS6", "SS7", "SS8", "SS10", "SS11", "SS12", "SS14")

stage_codes =  unlist(stage_list)
last_stage_code = stage_codes[length(stage_codes)]

# Just in case
stage_list = unique(stage_list)

omit_stage_splits = c()

cutoff_delta = -1 #1500000 # if negative ignore

src = knit_expand("overall-template.Rmd")
cat(knit_child(text=src,
               options = list(echo=FALSE, warning=FALSE, error=FALSE),
               quiet=TRUE))
```

# Overall Driver Reports {-}

Summary reports over all completed stages, rebased to each driver.

```{r looper_overall_driver, message=FALSE, echo=FALSE,error=FALSE, warning=FALSE, results='asis'}
for (driverEntryId in wrc_entries){
    #driverEntryId=22431
    driverCode = cars[cars$entryId==driverEntryId, 'code']
    
    # Remove accents for use in chunk labels/image names
    driverCodeClean = stringi::stri_trans_general(driverCode, "Latin-ASCII")
    
    template = "driver_overall_template.Rmd"
    #template="empty_template.Rmd"
    src = knit_expand(template)
    cat(knit_child(text=src,
                     options = list(echo=FALSE, warning=FALSE, error=FALSE),
                     quiet=TRUE))
    
  }
```

# Loop Reports {-}

*Forthcoming... summary reports for each loop.*

```{r echo=FALSE}
#Folded text example: https://stackoverflow.com/a/53812694/454773
```
<style>
.fold-btn { 
  float: right; 
  margin: 5px 5px 0 0;
}
.fold { 
  border: 1px solid black;
  min-height: 40px;
}
</style>

<script type="text/javascript">
$(document).ready(function() {
  $folds = $(".fold");
  $folds.wrapInner("<div class=\"fold-blck\">"); // wrap a div container around content
  $folds.prepend("<button class=\"fold-btn\">Unfold</button>");  // add a button
  $(".fold-blck").toggle();  // fold all blocks
  $(".fold-btn").on("click", function() {  // add onClick event
    $(this).text($(this).text() === "Fold" ? "Unfold" : "Fold");  // if the text equals "Fold", change it to "Unfold"or else to "Fold" 
    $(this).next(".fold-blck").toggle("linear");  // "swing" is the default easing function. This can be further customized in its speed or the overall animation itself.
  })
});
</script>

<div class="fold">
Loop reports will provide summaries and views over stage results on a *per loop* basis.
</div>

```{r looper, message=FALSE, echo=FALSE, error=FALSE, warning=FALSE, results='asis'}

#stage_list=list("SS1","SS2")
for (stage_code in stage_list){
  stageId = stages_lookup[[stage_code]]
  stage_times = get_stage_times(eventId, stageId)

  stage_info_ = stage_info[stage_info['stageId']==stageId,]
 
  src = knit_expand("stage_result_template.Rmd")
  cat(knit_child(text=src,
                 options = list(echo=FALSE, warning=FALSE, error=FALSE),
                 quiet=TRUE))
}
```

```{r persist_data_multi_overall, echo=FALSE}
#save_data(multi_overall_results, "multi_overall_results.csv")
#save_data(multi_stage_times, "multi_stage_times.csv")
```

```{r end_logger, echo=FALSE}
cat("Finished build", file=logFile, sep='\n')
```
