```{r warning=FALSE, include=FALSE, echo=FALSE, message=FALSE}
library(sparkline)
library(kableExtra)
source('overall_sketches.R')
source('spark_sketches.R')
```

```{r}
stage_codes =  unlist(stage_list)
stage_list_codes = stages[stages$code %in% stage_codes, 'stageId']
```

```{r overall_wide_gap, echo=FALSE, message=FALSE, warning=FALSE, include=FALSE}
# TO DO - reorder the order of display of tables

# TO DO  - gap to leader at end of stage


# TO DO - we need to make sure we are working with the same cars
# For example, WRC cars (cars in group), top 10 overall etc
# The top 10 by stage may not be the same as top 10 overall


multi_overall_results = get_multi_overall(stage_list_codes) %>%
                            mutate(diffFirstS = diffFirstMs/1000,
                                   totalTimeS = totalTimeMs/1000) %>%
                          filter(entryId %in% wrc_entries) 

# Optionally, re-rank by group by stage
if (use_group_rank) {
  #multi_overall_results$overall_position = multi_overall_results$position
  multi_overall_results = multi_overall_results %>%
                            group_by(stageId) %>%
                            mutate(overall_position = position,
                                   position = rank(position))
}

multi_overall_wide_pos = multi_overall_results %>%
                            get_multi_stage_generic_wide(stage_list_codes,
                                                         'position') %>%
              dplyr::arrange(!!as.symbol(stage_list_codes[length(stage_list_codes)]))


multi_overall_wide_time = multi_overall_results %>%
                              get_multi_stage_generic_wide(stage_list_codes,
                                                           'totalTimeS') %>%
              dplyr::arrange(!!as.symbol(stage_list_codes[length(stage_list_codes)]))

# TO DO - we need to be able to use the gap to group leader not overall
# Maybe have a re-rebase?
multi_overall_wide_gap = multi_overall_results %>%
                            get_multi_stage_generic_wide(stage_list_codes,
                                                         'diffFirstS') %>%
              dplyr::arrange(!!as.symbol(stage_list_codes[length(stage_list_codes)]))

if (use_group_rank) {
  group_rebase_id = multi_overall_wide_gap$entryId[1]
  multi_overall_wide_gap = multi_overall_wide_gap %>%
                            rebase(group_rebase_id, stage_list_codes)
}

# Based around entryId: 
# multi_overall_wide_pos, multi_overall_wide_time, multi_overall_wide_gap
```


```{r overall_multi_stage, warning=FALSE, include=FALSE, echo=FALSE, message=FALSE}
# TO DO - need to have a function that does WRC/class not overall top10
clean_top10 = function(df) {
  df %>% relabel_times_df(stage_list_codes, cars) %>%
          dplyr::arrange(!!as.symbol(stage_codes[length(stage_codes)])) %>%
          head(20)
}          

multi_stage_times = get_multi_stage_times(stage_list_codes)  %>%
                          filter(entryId %in% wrc_entries)


# Optionally, re-rank by group
if (use_group_rank) {
  multi_stage_times = multi_stage_times %>%
                            group_by(stageId) %>%
                            mutate(overall_position = position,
                                   position = rank(position))
}

# We need to add entryId back in here
multi_stage_times_wide = multi_stage_times %>%
                            get_multi_stage_times_wide(stage_list_codes) %>%
                    dplyr::arrange(!!as.symbol(stage_list_codes[length(stage_list_codes)]), na.last=TRUE) %>%
clean_top10()

multi_stage_wide_pos = multi_stage_times %>%
                              get_multi_stage_generic_wide(stage_list_codes,
                                                         'position')  %>%
                dplyr::arrange(!!as.symbol(stage_list_codes[length(stage_list_codes)]), na.last=TRUE) %>%
                            clean_top10()
```



```{r }
# TO DO - colour an improvement green, a loss red
out_table = multi_overall_wide_pos %>%
                              map_stage_codes(stage_list_codes) %>%
                              map_driver_names(cars) %>% 
              dplyr::arrange(!!as.symbol(stage_codes[length(stage_codes)]))  %>%
              select(-entryId) %>% head(10)
```



```{r}
overall_rebase_code = out_table$code[1]
  
multi_overall_wide_gap_top10 = multi_overall_wide_gap %>%
                              map_driver_names(cars) %>%
                              rebase(overall_rebase_code,
                                     stage_list_codes, id_col='code') %>%
                              map_stage_codes(stage_list_codes) %>%
        dplyr::arrange(!!as.symbol(stage_codes[length(stage_codes)]), na.last=TRUE) %>%
      # TO DO - filter on entryID NOT code - du0licates etc NEU
      # Hackfix limit on top 20 for pool for now...
      head(20) %>%
      filter(code %in% out_table$code) 
                      #head(10)
```




```{r}
gt_stage_pos_plots = list()
multi_stage_long_pos = multi_stage_wide_pos %>%
                              pivot_longer(c(all_of(stage_codes)),
                                           names_to ="Stage",
                                           values_to ="Pos") %>%
                          mutate(Stage = factor(Stage,
                                                levels = stage_codes))

# TO DO - add Overall with coloured background?
#formattable(multi_stage_wide_pos, align='c',
#                  list(area(col = stage_codes) ~ highlight_first())) 

```


```{r message=FALSE}
overall_long_gap_top10 <- multi_overall_wide_gap_top10 %>%
                            # Make relative to current overall leader
                            # at end of each stage
                            mutate_at(2:ncol(multi_overall_wide_gap_top10),
                                      list(~ . + abs(min(., na.rm=TRUE)))) %>% 
                            gather(key ="Stage",
                            value ="Gap", all_of(stage_codes)) %>%
                                group_by(code) %>%
                                summarize(spk_ = spk_chr(-Gap,
                                                         type ="bar")) %>%
                              rename(overall_gap_bar=spk_)
#spark_df(overall_long_gap_top10)
```

```{r warnining=FALSE}
# Gap to stage winner

min2 = function(x, na.rm = TRUE) x - min(x, na.rm = na.rm)
                                  
# If we are in the group, we need to use diffFirstMs *in group*
multi_stage_wide_gap = multi_stage_times %>%
                            mutate(diffFirstS = diffFirstMs/1000) %>%
                            get_multi_stage_generic_wide(stage_list_codes,
                                                         'diffFirstS')  %>%
                            relabel_times_df(stage_list_codes, cars) %>%
          dplyr::arrange(!!as.symbol(stage_codes[length(stage_codes)])) %>%
  # calculate within group diff pn the diffFirst
  mutate_at(stage_codes, min2) %>% 
  # Hackfix - name  duplicate
  head(20) %>%
  filter(code %in% overall_long_gap_top10$code) 


#multi_stage_wide_gap


multi_stage_long_gap = generate_spark_bar(multi_stage_wide_gap) %>%
  rename(gap_to_stagewinner_bar=spk_)

#spark_df(multi_stage_long_gap)
```


```{r warning=FALSE, message=FALSE}
# Stage position chart
#top10_codes = multi_stage_wide_pos$code
multi_overall_wide_pos_ = multi_overall_wide_pos  %>%
                            relabel_times_df(stage_list_codes, cars) %>%
          dplyr::arrange(!!as.symbol(stage_codes[length(stage_codes)])) %>% head(10)

multi_overall_long_pos = multi_overall_wide_pos_ %>%
                              pivot_longer(c(all_of(stage_codes)),
                                           names_to ="Stage",
                                           values_to ="Pos") %>%
                          mutate(Stage = factor(Stage,
                                                levels = stage_codes))

top10_codes = multi_overall_wide_pos_$code
gt_stage_pos_plots = list()
gt_overall_pos_plots = list()
# Iterate through each driver in the top 10
for (c in 1:length(top10_codes)){
    # Add each plot to the plot list
    gt_stage_pos_plots[[length(gt_stage_pos_plots) + 1]] <-
        get_pos_chart(multi_stage_long_pos, top10_codes[c],
                      embed=T, aspect_ratio=3, size=5)
    gt_overall_pos_plots[[length(gt_overall_pos_plots) + 1]] <-
        get_pos_chart(multi_overall_long_pos, top10_codes[c],
                      embed=T, aspect_ratio=3, size=5)
}

multi_overall_wide_pos_$stage_poschart = gt_stage_pos_plots
```


```{r warning=FALSE, message=FALSE}
#position changes
pos_codes = multi_overall_wide_pos_$code

# This doesn't apply for just SS1
pos_diffs = multi_overall_wide_pos_ 
if (length(stage_list) > 1) {
  pos_diffs = pos_diffs %>% 
                  select(-code) %>%
                  coldiffs(all_of(stage_codes),firstcol=0)
  pos_diffs$code = pos_codes
  
  # Reorder the columns by moving last column to first
  #pos_diffs = pos_diffs %>% select('code', everything())
}

pos_gains = pos_diffs

pos_gains[,stage_codes] = -pos_gains[,stage_codes]

pos_gain_long_top10 <- pos_gains %>%
                              head(10) %>%
                              gather(key ="Stage",
                                     value ="PosChange",
                                      all_of(stage_codes))

pos_gain_sparkline_top10 <- pos_gain_long_top10 %>%
                                group_by(code) %>%
                                summarize(spk_ = spk_chr(PosChange,
                                                         type ="bar")) %>%
                            rename(pos_change_bar=spk_)

#pos_gain_sparkline_top10 %>% spark_df()
```

```{r}
multi_overall_wide_pos_$overall_poschart = gt_overall_pos_plots
```

```{r warning=FALSE }
# Stage Pace Calculations

stage_range = c(start=stage_codes[1],
                end=stage_codes[length(stage_codes)])


multi_stage_pace = get_multi_stage_pace(multi_stage_times, cars)

# TO DO - we need to rebase to group leader
# TO DO get_multi_stage_generic_wide() should fail nice w/ empty df
# WRC sucks with duplicate driver codes...
# So need to back up and include the driverId
pace_wide = multi_stage_pace %>% 
              get_multi_stage_generic_wide(stage_codes, 'pace',
                                           # Unique group keys required
                                           # Driver code not guaranteed unique
                                           group_key=c('code_driver', 'entryId'),
                                           spread_key='code')

overall_lead_code = multi_overall_wide_pos_[1, 'code']

pace_wide_rebased = rebase(pace_wide, overall_lead_code, stage_codes,
                           id_col='code_driver')

pace_stage = pace_wide_rebased %>% 
                gather(code, pace,
                       stage_range['start']:stage_range['end']) %>%
                merge(stages[,c('code', 'start_dist', 'cum_dist')],
                          by='code')
```

## Rally Sparkline Summary

Simple summary charts of rally progress for each driver, ordered by latest overall ranking:

```{r}
# Don't display if only a single stage
if (length(stage_list)>1) {
  multi_overall_wide_gap_top10['code'] %>%
    inner_join(multi_overall_wide_pos_[,c('code','overall_poschart')], by = 'code') %>%
    inner_join(overall_long_gap_top10, by = 'code') %>%  
      inner_join(pos_gain_sparkline_top10[, c('code','pos_change_bar')], by = 'code') %>%
   inner_join(multi_overall_wide_pos_[,c('code','stage_poschart')], by = 'code') %>%
  inner_join(multi_stage_long_gap[, c('code','gap_to_stagewinner_bar')], by = 'code') %>%
  rename("Overall Pos"=overall_poschart, "Overall Gap"=overall_gap_bar,
         "Stage Pos"= stage_poschart, "Stage Gap"=gap_to_stagewinner_bar,
         "Overall Pos Change"=pos_change_bar) %>%
  spark_df()
} else cat('Not enough data for a meaningful table...')
#TO DO - need to be able to pass in a caption to spark_df
```



## Off-the-Pace Chart

Overall time deltas at each stage relative to overall leader:

```{r overall-off-the-pace-chart, warning=FALSE, message=FALSE}
g = multi_overall_wide_gap_top10 %>%
        pivot_longer(!code, names_to = "Num", values_to = "time") %>%
        filter(abs(time)<=300 ) %>%
        mutate(Num = as.integer(str_replace(Num, "SS", ""))) %>%
        off_the_pace_chart(dist='Num',
                           t='time',
                           #label_typ='ggrepel',
                           code='code', yflip=TRUE)

g + labs(title = paste0("Off-the-pace chart for overall leader"),
  subtitle = paste0("Time gained / lost over stages, ", rally_name),
  x="Stage",
  y="Time delta (s)",
  caption = "Created by: RallyDataJunkie.com" # eg WRC Rally
) 
```

*TO DO - this is misleading. Drivers fall of the pace are dropped the chart but the chart should show the line going off the chart.*


## Stage Pace

Stage pace charts rebased to overall leader.

```{r overall-stage-pace-chart, warning=FALSE}
# Need ylim to make sure all the leaders pace comparisons
# with lost time are in view

cum_dist = max(pace_stage$cum_dist)
g_pm = pace_map(pace_stage, label_size=2,
                pace_label_offset=-0.04) #+ ylim(1.5, -1.5)


# Add banner - TO DO  - this generates warnings... Need to tidy up
g_pm = g_pm  +
    theme(legend.position="none") + 
  labs(title = paste0("Pace chart across stages" ),
  subtitle = paste0("Rebased relative to overall leader (",overall_lead_code,"), ", rally_name),
  x="Accumulated stage distance (km)",
  y="Pace delta (s/km)",
  caption = "Created by: RallyDataJunkie.com"

) 

ypace_limits = layer_scales(g_pm)$y$get_limits()
ypace_max = abs(ypace_limits[1])
ypace_min = ifelse((abs(ypace_max) < 1.5), -1.5, -abs(ypace_max))

g_pm + geom_rect(data=pace_stage[pace_stage$code_driver==overall_lead_code,],
              aes(xmin=0, xmax=max(cum_dist),
                  ymin = ypace_min-0.2,  ymax = ypace_min-0.4,
                  alpha=0), fill = 'black') +
    geom_text(data=pace_stage[pace_stage$code_driver==overall_lead_code,],
              aes(x=(cum_dist + start_dist)/2, label=code),
              y=abs(ypace_min-0.3), color='yellow', size=3) +
    geom_segment(data=pace_stage[pace_stage$code_driver==overall_lead_code,],
                 aes(x=cum_dist, xend=cum_dist,
                    y=ypace_min-0.2, yend=ypace_min-0.4), color='yellow') +
    geom_segment(data=pace_stage[pace_stage$code_driver==overall_lead_code,],
                 aes(x=cum_dist, xend=cum_dist,
                    y=ypace_max, yend=ypace_min-0.4),
                 linetype="dotted",
                 color='lightgrey') + ylim(ypace_max, ypace_min-0.4)
```

*TO DO - the fastest pace line should have a purple colour.*


## Gap to Overall Leader at Each Stage End

The gap to the overall leader at the end of each stage, with table ordered by overall rally position at end of last recorded stage:

```{r}
#kable(multi_overall_wide_gap_top10)
# Add min value abs to each column
multi_overall_wide_gap_top10_view = multi_overall_wide_gap_top10 %>% mutate_at(2:ncol(multi_overall_wide_gap_top10), list(~ . + abs(min(., na.rm=TRUE))))

kable(multi_overall_wide_gap_top10_view, format = "html") %>%
  kable_styling() %>%
  kableExtra::scroll_box(width = "100%")
```


## Stage Wins Summary

Summary of stage wins.

```{r warning=FALSE, message=FALSE}
# Count number of stage wins by driver
# If we have a tie then the pos is still ranked so rerank based on delta
multi_stage_wide_gap %>% 
  pivot_longer(!code, names_to = "Stage", values_to = "Delta") %>% filter(Delta==0) %>% select(c('code', 'Stage')) %>%
group_by(code) %>%  summarise(wins = toString(Stage), wincount=n()) %>% arrange(desc(wincount)) %>% formattable(align='c')

```


## Penalties

```{r}
controls = get_controls(sections)

map_controlId = function(df, controls){
  df %>%
    merge(controls[,c('controlId', 'code', 'location', 'type')],
          by='controlId', suffixes=c('', '2'))  %>%
    rename(control = code2)
}


penalties = get_penalties(eventId)

if (length(penalties)>0) {
  penalties = penalties %>%
    filter(entryId %in% wrc_entries)  %>% map_driver_names(cars) %>%
    map_controlId(controls) %>%
    mutate('penaltyDurationS' = penaltyDurationMs/1000 ) %>%
      # Limit columns and set column order
      select(-c(controlId, penaltyDurationMs, penaltyDurationMs,
                penaltyId, entryId)) %>%
      # Move last column to first
      select(code, control, location, type, reason, 'penaltyDurationS')
  
  penalties %>%
    formattable(caption=paste("Penalties", rally_name, sep=", "))
   # select(code, penaltyDuration, reason)
}
```

## Retirements

```{r}
retirements = get_retirements(eventId)

if (length(retirements>0)) {
  retirements %>%
  filter(entryId %in% wrc_entries)  %>% map_driver_names(cars) %>%
  map_controlId(controls) %>% 
  rename(time=retirementDateTime) %>%
  select(-c(controlId, retirementId, retirementDateTimeLocal, entryId)) %>%
  relocate(reason, .after = last_col()) %>%
  formattable(caption=paste("Retirements", rally_name, sep=", "))
}

```


## Stage Position History

*Ranked according to position on last recorded stage __not__ overall position. The advantage of this ordering is that it helps register "surprise" arising from a perhaps unexpected stage winner. The chart gives the summary of stage rank evolution.*

*Note that the stage position is based on the positions given by WRC Live Timing. If two drivers record the same time (or at least, same time to a tenth of a second), only one of them will have position==1 and the other will be position==2. A different "first" truth can be generated by testing on gap==0.0.*

```{r}
# Order according to overall
overall_order = multi_overall_wide_pos_$code
kable(multi_stage_wide_pos %>% dplyr::arrange(factor(code, levels = overall_order)), format = "html") %>%
  kable_styling() %>%
  kableExtra::scroll_box(width = "100%")
```


## Stage Times

Summary of raw stage times

```{r}
#kable(multi_stage_times_wide)
kable(multi_stage_times_wide %>%
        dplyr::arrange(factor(code, levels = overall_order)) %>%
        select(-entryId), format = "html")  %>%
  kable_styling() %>%
  kableExtra::scroll_box(width = "100%")
```

## Stage Time Deltas

Summary of stage time deltas (*gap* to stage winner in seconds):

```{r}
#kable(multi_stage_times_wide)
multi_stage_win_gap_ordered = multi_stage_wide_gap %>%
        dplyr::arrange(factor(code, levels = overall_order))  %>%
        select(-entryId)

kable(multi_stage_win_gap_ordered, format = "html")  %>%
  kable_styling() %>%
  kableExtra::scroll_box(width = "100%")
```

## Stage Win Truth

Originally developed to support the automated text summary production, the *stage win truth* table provides a glanceable view summarising the stage winner on each stage:

```{r}
#ifelse(is.na(x), FALSE, x)
isStageWin = function(x) ifelse(is.na(x), FALSE, x==0)

multi_stage_win_truth = multi_stage_win_gap_ordered %>%
                          mutate(across(stage_codes, isStageWin))

multi_stage_win_truth
```

## Overall Position

Evolution of overall position:

```{r}
#formattable(out_table,
#            align='c',
#                  list(area(col = stage_codes) ~ highlight_first()))
#kable(out_table)
kable(out_table, format = "html") %>%
  kable_styling() %>%
  kableExtra::scroll_box(width = "100%")
```

## Overall Lead Truth

Originally produced to support text summary generation, the *overall lead truth* tables  provide glanceable views over how the overal lead developed over each stage.

Truth tables include glanceable reviews of the overall leader, as well as overall lead gains, losses and retention.

Overall lead truth (based on gap to leader of 0s to capture joint stage times at the level of tenths of a second):

```{r}
#ifelse(is.na(x), FALSE, x)
isLead = function(x) ifelse(is.na(x), FALSE, x==1)
pos_delta = function(curr, prev) {
  #Positive is improvement, negative is loss 
  prev-curr
}
out_table %>% mutate(across(stage_codes, isLead))
```



```{r}
last_stage_code = stage_codes[length(stage_codes)]

multi_overall_lead_previous_long = out_table %>% pivot_longer(cols = -c(code), names_to = "stage", values_to = "position")  %>%
  group_by(code) %>%
  mutate(prev_position = lag(position, order_by=code),
         retained_lead=isLead(position) & isLead(prev_position),
         lost_lead=!isLead(position) & isLead(prev_position),
         gained_lead=isLead(position) & !isLead(prev_position))

multi_overall_lead_previous_long = multi_overall_lead_previous_long %>%
                mutate(overall_position_delta=pos_delta(position, prev_position))  %>%
 group_by(stage) %>%
 mutate(overall_chase_code = lead(code, order_by=position),
        overall_lead_code = lag(code, order_by=position))
```

Overall position in previous stage:

```{r}
multi_overall_lead_previous_wide = multi_overall_lead_previous_long %>%
  pivot_wider(id_cols=c(code), names_from=stage, values_from=prev_position)
multi_overall_lead_previous_wide
```

Retained overall lead:

```{r}
multi_overall_lead_retained_wide = multi_overall_lead_previous_long %>%
  pivot_wider(id_cols=c(code), names_from=stage,
              values_from=retained_lead)

multi_overall_lead_retained_wide
```

Lost overall lead:

```{r}
multi_overall_lead_lost_wide = multi_overall_lead_previous_long %>%
  pivot_wider(id_cols=c(code), names_from=stage,
              values_from=lost_lead)

multi_overall_lead_lost_wide
```

Gained overall lead:

```{r}
multi_overall_lead_gained_wide = multi_overall_lead_previous_long %>%
  pivot_wider(id_cols=c(code), names_from=stage,
              values_from=gained_lead)

multi_overall_lead_gained_wide
```
Stage winner gained overall lead

```{r}
tmp_truth = data.frame((multi_stage_win_truth %>% select(!code)) & multi_overall_lead_gained_wide %>% select(!code))

multi_overall_stagewin_lead_gained_wide = multi_stage_win_truth %>%
  select(code)%>%  cbind(tmp_truth)

multi_overall_stagewin_lead_gained_wide
```

## Gap to the Driver in Overall Lead at Each Stage End

The gap to current overall leader, `r overall_lead_code`, with table ordered by overall rally position at end of last recorded stage:

```{r}
#kable(multi_overall_wide_gap_top10)
kable(multi_overall_wide_gap_top10, format = "html") %>%
  kable_styling() %>%
  kableExtra::scroll_box(width = "100%")
```

## Text report

```{r message=FALSE, results='hide'}
library(reticulate)

py_run_file("rules_processor.py")
py_run_file("rules_overall.py")

```

```{r}
overall_reporter_view = multi_overall_lead_previous_long %>% 
         filter(stage==!!last_stage_code)  %>%
         merge(multi_overall_wide_gap_top10_view %>% 
                select(code, !!last_stage_code) %>%
                rename(overall_gap=!!last_stage_code), by='code')  %>%
         merge(multi_stage_wide_pos %>% 
                select(code, !!last_stage_code) %>%
                rename(stage_position=!!last_stage_code), by='code')  %>%
         merge(multi_stage_win_truth %>% 
                select(code, !!last_stage_code) %>%
                rename(stage_win=!!last_stage_code), by='code') %>% 
         rename(overall_pos = position) %>%
         dplyr::arrange(overall_pos) %>%
         mutate(overall_diff=overall_gap-lag(overall_gap),
                overall_chase=lead(overall_gap)-overall_gap) %>%
        mutate(stagenum = str_extract(stage,"\\d+"))

if (length(penalties)>0)
   overall_reporter_view = overall_reporter_view %>% 
        left_join(penalties %>% mutate(stagenum = str_extract(control,"\\d+")), by=c('stagenum', 'code'))

# TO DO - it would be useful to have the gap/diff change from each stage 
# Also, whether the person ahead or behind is in the same position

kable(overall_reporter_view, format = "html") %>%
  kable_styling() %>%
  kableExtra::scroll_box(width = "100%")
```
```{r message=FALSE, results='hide'}
src = knit_expand("rule_template_overall.Rmd")
knit_child(text=src,
               options = list(echo=FALSE,results='hide', warning=FALSE, error=FALSE),
               quiet=TRUE)
```

__Overall rally report at end of `r last_stage_code`:__

```{r results="asis"}
cat(py$txt_out)
```

```{r results="asis"}
#if ("NEU" %in% names(py$overall_txts))
#  cat(paste('NEU: ',py$overall_txts[["NEU"]]))
```