```{r}
cat(paste("test-template IN: ",stage_code),
    file=logFile, append=TRUE, sep = "\n")
```

## Stage `r stage_code` Splits Analysis

Reports on splits

```{r fsd-{{result_group}}-{{stage_code}}, cache=TRUE, results=FALSE, message=FALSE, warning=FALSE}
#library(formattable)

#stage_code = 'SS6'
#stageId = stage_list_codes[1]

splits = get_splits(eventId, stageId)

splits_locations = splits$splitPoints %>% arrange(number)
splits_list = splits_locations$splitPointId
splits_locations$splitname = sapply(splits_locations$splitPointId,
                                 get_split_label)

split_names = splits_locations$splitname
split_cols = get_split_cols(splits)
split_names = c(split_names, 'split_N')

# Split distances
splits_locations$start_dist = lag(splits_locations$distance,
                                  default=0)

splits_locations$section_dist = c(splits_locations$distance[1],
                                  diff(splits_locations$distance))
split_distances = splits_locations$section_dist

stage_dist = stages[stages['stageId']==stageId,'distance']
full_split_distances = c(split_distances, stage_dist-sum(split_distances))
# Label distances using split names
names(full_split_distances) = split_names
full_split_distances_df = full_split_distances %>%
                              as.data.frame() %>%
  tibble::rownames_to_column() %>%
                              mutate(distance=cumsum(full_split_distances)) %>%
 select(c(rowname, distance)) %>% rename(splitname=rowname)
```

```{r fsw--{{result_group}}-{{stage_code}}, cache=TRUE, echo=FALSE, message=FALSE, warning=FALSE,}
full_splits_wide = get_splits_wide(splits, wrc_entries) %>%
                      widen_splits_stage_times(stage_times) %>%
                      filter(entryId %in% wrc_entries) %>%
                      map_split_codes(splits_list) %>% 
                      map_driver_names(cars)  %>%
                      arrange(position)

if (use_group_rank) {
  group_rebase_id = full_splits_wide$code[1]
  full_splits_wide = full_splits_wide %>%
                            rebase(group_rebase_id, 'diffFirstMs', 
                                   id_col='code')
}


#save_data(full_splits_wide, paste0("full_splits_wide", stage_code, ".csv"))

#kable(full_splits_wide)
```


```{r}
# Filter out any driver with an excessive delta
#https://dplyr.tidyverse.org/reference/filter_all.html
#filter_at(vars(starts_with("split_")),
#          all_vars(abs(.) <20))

# TO DO - would it make more sense to cutoff from a large gap?
if (!(exists("cutoff_delta"))) cutoff_delta = 30000
if (cutoff_delta>0)
  full_splits_wide = full_splits_wide %>%
                        filter(diffFirstMs<cutoff_delta)
```


```{r echo=FALSE, message=FALSE, warning=FALSE}
full_durations_wide = get_split_duration(full_splits_wide,
                                          split_names, id_col='code')

# Pace
section_pace_wide = full_durations_wide

for (s in split_names) {
  section_pace_wide[,s] = section_pace_wide[,s] / full_split_distances[s]
}

#save_data(full_durations_wide, paste0("full_durations_wide", stage_code, ".csv"))
```

### Split Locations

Length of each split section in km:

```{r}
dist_df = data.frame(full_split_distances) %>% 
              mutate(stage_dist = cumsum(full_split_distances))

#save_data(dist_df, paste0("split_distances", stage_code, ".csv"))
kable(dist_df)
```


### Stage Split Times & Result

Summary of stage split times and overall stage result:

```{r}
stage_split_results = full_splits_wide %>% 
                  mutate(diffFirstS=diffFirstMs/1000) %>% 
                  select(c(code,  all_of(split_names),
                         diffFirstS, position)) %>% 
                  arrange(position)

kable(stage_split_results)
```

### Split Time Rankings

Rank of each split time:

```{r echo=FALSE, message=FALSE, warning=FALSE, error=FALSE}
split_ranks = get_split_rank(full_splits_wide, split_names) %>%
                select(code, all_of(split_names) ) %>%
                filter_at(vars(starts_with("split_")),
                                all_vars(! is.na(.)))

split_N_col_idx = which(colnames(split_ranks) == 'split_N')[[1]]

caption = paste0(stage_info_$code, ' split time rank')

formattable(split_ranks, align='c',
            list(area(col = 2:split_N_col_idx) ~ color_tile2(c("red",'white', "forestgreen")),
                 entryId=FALSE), caption=caption)
```

Rank on each split section:

```{r}
split_duration_ranks = get_split_rank(full_durations_wide, split_names)

caption = paste0(stage_info_$code, ' split section rank')
formattable(split_duration_ranks, align='c',
            list(area(col = 2:split_N_col_idx) ~ color_tile2(c("red",'white', "forestgreen")),
                 entryId=FALSE), caption=caption)
```

### Split Section Pace

Pace is measured in seconds per kilometer, which is to say, how long it takes to complete each kilometer (*lower is better*):

```{r}
kable(section_pace_wide %>% mutate_if(is.numeric, round, digits = 2) )
```

### Pace Chart

Pace relative to the stage winner.

```{r test-pace-chart-{{result_group}}-{{stage_code}}, cache=TRUE}
stage_winner_code = section_pace_wide[1,]$code
full_split_distances_df = full_split_distances_df %>% 
                            mutate(start_dist =lag(distance, default=0))

section_pace_wide_rebased = rebase(section_pace_wide, stage_winner_code,
                                   split_names, id_col='code')


section_pace_long_rebased = section_pace_wide_rebased %>% 
                  head(10) %>%
                gather(splitname, pace,
                       as.character(split_names)) %>%
                merge(full_split_distances_df[,c('splitname',
                                          'start_dist', 'distance')],
                      by='splitname')

section_pace_long_rebased %>%
    pace_map( xstart='start_dist', id_col='code',
         xend='distance', lines=FALSE, label_dodge=2,
         label_size=2) + xlab("Accumulated stage distance (km)") + ylim(1.5, -1.5) + labs(title = paste0("Pace chart over splits, ", stage_code),
  subtitle = paste0("Rebased relative to stage winner (",stage_winner_code,"), ", rally_name),
  x="Distance into stage (km)",
  y="Pace delta (s/km)",
  caption = "Created by: RallyDataJunkie.com" ) 
                
```

### Ultimate Stage Comparisons

Split time comparisons relative to various ultimate stage time calculations.

These views provide various ways of comparing the performance of each driver to various ghost drivers:

- best recorded split time at each split (*ultimate actuals*): gives an estimate of how well the driver's split times compare with each first ranked split time (time into stage at each split);
- fastest time going from one split to the next (*ultimate sections*): gives an estimate of how quickly each driver completed each split section relative to the quickest time recorded completing that split section (time taken to go from one split point to the next);
- *accumulated ultimate sections* times: gives and estimate of how quickly the driver is going relative to the fastest possible completion of the stage based on accumulated ultimate split section times.

```{r test-ults-{{result_group}}-{{stage_code}}, cache=TRUE, echo=FALSE, message=FALSE, warning=FALSE}
ultimate_splits_long = full_durations_wide %>%
                     pivot_longer(all_of(split_names),
                                  names_to = "splitname",
                                  values_to = "sectionDurationS") %>%
                     select(splitname, sectionDurationS) %>%
                     # Defensive measure
                     #filter(!is.na(sectionDurationS) & sectionDurationS>0) %>%
                     group_by(splitname) %>% 
                     summarise(ultimate = min(sectionDurationS,
                                              na.rm = TRUE)) %>%
                     mutate(ultimateElapsed = cumsum(ultimate))

ultimate_wide_durations = ultimate_splits_long %>% 
                  select(splitname, ultimate) %>%
                  pivot_wider(names_from = splitname,
                              values_from = ultimate) %>%
                  mutate(code='ultimate')

ultimate_between_split = full_durations_wide %>%
                            select(code, all_of(split_names)) %>% 
                            bind_rows(ultimate_wide_durations) %>%
                            rebase('ultimate', split_names,
                                   id_col='code')

ultimate_wide_elapsed = ultimate_widen(ultimate_splits_long,
                                       'ultimateElapsed', 'ultimate')

ultimate_accumulated = full_splits_wide %>% 
                          ultimate_rebaser(ultimate_wide_elapsed,
                                         split_names, 'ultimate')

actual_ultimate = full_splits_wide %>% 
                      select(code, all_of(split_names)) %>% 
                      # Make long
                      select(all_of(as.character(split_names)),
                             code) %>%
                      pivot_longer(as.character(split_names),
                                   names_to = "splitname",
                                   values_to = "sectionDurationS") %>%
                      group_by(splitname) %>%
                      summarise(actualUltimate = min(sectionDurationS,
                                                     na.rm=TRUE))

ultimate_splits_long$actual = actual_ultimate$actualUltimate
ultimate_wide_actual = ultimate_widen(ultimate_splits_long,
                                      'actual',
                                      'ultimate')
ultimate_actual = full_splits_wide %>% 
                      ultimate_rebaser(ultimate_wide_actual,
                                       split_names, 'ultimate')

```

#### Ultimate Actuals

Driver times compared to the first ranked recorded split time at each split:

```{r ult-act-table-{{result_group}}-{{stage_code}}, cache=TRUE}
caption = paste0(stage_info_$code, ' ultimate split actual deltas')
ultimate_actual %>%
                  filter_at(vars(starts_with("split_")),
                                all_vars(! is.na(.)))  %>%
        mutate_if(is.numeric, round, digits = 1) %>%
formattable( align='c',
            list(area(col = 2:split_N_col_idx) ~ color_tile2(c("red",'white', "forestgreen")),
                 entryId=FALSE), caption=caption)
```


#### Ultimate Sections

Split durations rebased relative to the fastest transit of each split section:

```{r echo=FALSE, message=FALSE, warning=FALSE}
caption = paste0(stage_info_$code, ' ultimate section deltas')
ultimate_between_split %>%
                  filter_at(vars(starts_with("split_")),
                                all_vars(! is.na(.)))   %>%
      mutate_if(is.numeric, round, digits = 1) %>%
formattable(align='c',
            list(area(col = 2:split_N_col_idx) ~ color_tile2(c("red",'white',"forestgreen")),
                 entryId=FALSE), caption=caption)
```


#### Ultimate Accumulated Sections

Actual split times relative to the accumulated ultimate split section times:

```{r test-uas-t-{{result_group}}-{{stage_code}}, cache=TRUE,}
caption = paste0(stage_info_$code, ' accumulated ultimate section deltas')
ultimate_accumulated %>%
                  filter_at(vars(starts_with("split_")),
                                all_vars(! is.na(.)))  %>%
        mutate_if(is.numeric, round, digits = 1) %>%
formattable( align='c',
            list(area(col = 2:split_N_col_idx) ~ color_tile2(c("red",'white', "forestgreen")),
                 entryId=FALSE), caption=caption)
```

### Split Section Pace Distribution

Distribution of pace values for each split section:

```{r test-split-pace-chart-{{result_group}}-{{stage_code}}, cache=TRUE, warning=FALSE, error=FALSE, message=FALSE}
full_split_dists = map_df(full_split_distances, ~as.data.frame(.x), .id="splitname") %>% rename(section_distance = .x) %>% 
  mutate(distance = cumsum(section_distance))
#Pace calculation
section_pace_long = section_pace_wide %>% 
                  head(10) %>%
                gather(splitname, pace, split_names) %>%
                #merge(splits_locations[,c('splitname',
                #                          'start_dist', 'distance')],
                merge(full_split_dists,
                          by='splitname')

# TO DO start_dist as a lag...
# TO DO - the pace limit should be better set?
#ggplot(section_pace_long[section_pace_long$pace<40,],
ggplot(section_pace_long,
       aes(x=distance, y=pace)) +
    geom_boxplot(aes(group=distance)) +theme_bw() +
labs(title = paste0(stage_code, ": pace on each split"),
  subtitle = paste0("Boxplot depicting median and inter-quartile range, ", rally_name),
  x="Split distance into stage (km)",
  y="Pace (s/km)",
  caption = "Created by: RallyDataJunkie.com" )
```

```{r}
cat(paste("test-template OUT: ",stage_code),
    file=logFile, append=TRUE, sep = "\n")
```